Supporting Information:\\Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-12-18 Manuscript/SI.tex
Updated plots after OPC3->SPCE correction in simulations with cat.surf. According changes in MS and SI.

@@

\begin{figure}[!hp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B-g3_L14-ECCL17_q80_sig89_CaCl_waterModels.pdf}
  \caption{\label{fig:ordPars_waterModels}
    Changes of head group and glycerol carbon $g_3$ order parameters, and P-N vector orientation of POPC bilayer
    as a function of CaCl$_2$ concentrations in bulk ($C_{ion}$) from ECC-POPC simulations at 313K with different
    water models (OPC \cite{Izadi14}, OPC3~\cite{Izadi16}, TIP3P~\cite{jorgensen83}, TIP3p-FB and TIP4p-FB~\cite{Wang2014}, and TIP4p/2005 \cite{Abascal2005})
    together with experimental data (DPPC (323~K) \cite{akutsu81} and POPC (313~K) \cite{altenbach84}). 
    Ion concentrations ($C_{ion}$) are calculated from the cation number density $C_{np}$
    at the farthest point from the lipid bilayer in the aqueous phase as [ion]=$C_{np}/0.602$.
  }
\end{figure}

>>>>

OpenMM simulations were run with 4~fs time step using 4 times heavier hydrogen atoms (mass subtracted from neighbouring atoms).

@@

\begin{figure}[!hp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B-g3_L14-ECCL17_q80_sig89_surf_waterModels_compar.pdf}
  \caption{\label{fig:ordPars_waterModels_surf}
    Changes of head group and glycerol carbon $g_3$ order parameters, and P-N vector orientation of POPC bilayer
    as a function of a molar fraction of the cationic surfactant dihexadecyldimethylammonium in a POPC bilayer
    from simulations with different water models (OPC3~\cite{Izadi16}, SPC/E~\cite{Berendsen1987})
    and experiments \cite{scherer89} at 313 K.
  }
\end{figure}

\begin{figure}[!hp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B-g3_L14-ECCL17_q80_sig89_CaCl_waterModels.pdf}
  \caption{\label{fig:ordPars_waterModels}
    Changes of head group and glycerol carbon $g_3$ order parameters, and P-N vector orientation of POPC bilayer
    as a function of CaCl$_2$ concentrations in bulk ($C_{ion}$) from ECC-POPC simulations at 313K with different
    water models (SPC/E~\cite{Berendsen1987}, OPC \cite{Izadi14}, OPC3~\cite{Izadi16}, TIP3P~\cite{jorgensen83}, TIP3p-FB and TIP4p-FB~\cite{Wang2014}, and TIP4p/2005 \cite{Abascal2005})
    together with experimental data (DPPC (323~K) \cite{akutsu81} and POPC (313~K) \cite{altenbach84}). 
    Ion concentrations ($C_{ion}$) are calculated from the cation number density $C_{np}$
    at the farthest point from the lipid bilayer in the aqueous phase as [ion]=$C_{np}/0.602$.
  }
\end{figure}
